A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)

### 2024-10-02 manuscript/manuscript.qmd
figure orientation

---
title: ""

@@

editor: visual
bibliography: references.bib
#csl: american-journal-of-epidemiology.csl

@@

library(here)
library(captioner)

@@

**Authors**: Janick Weberpals^1^, ..., Sebastian Schneeweiss^1^, Shirley V. Wang^1^

@@

[**Article type:**]{.underline} Original Research Article

@@

[**Keywords:**]{.underline} Real-World Evidence

@@

[**Competing Interests Statement:**]{.underline} Dr. Schneeweiss is participating in investigator-initiated grants to the Brigham and Women's Hospital from Boehringer Ingelheim, Takeda, and UCB unrelated to the topic of this study. He owns equity in Aetion Inc., a software manufacturer. He is an advisor to Temedica GmbH, a patient-oriented data generation company. His interests were declared, reviewed, and approved by the Brigham and Women's Hospital in accordance with their institutional compliance policies.

@@

@@

@@

# Results {#sec-results}

@@

\blandscape

@@

\elandscape

>>>>

---
title: "A Process for the Emulation of Comparative Oncology Trials with Real-world Evidence (ENCORE)"

@@

editor: visual
bibliography: references.bib
csl: journal-of-clinical-oncology.csl

@@

library(here)
library(knitr)
library(captioner)

@@

**Authors**: Janick Weberpals^1^, Donna R. Rivera^2^, ..., Sebastian Schneeweiss^1^, Shirley V. Wang^1^

@@

[**Article type:**]{.underline} Review

@@

[**Keywords:**]{.underline} Oncology, Real-World Evidence, Trial emulation, EHR

@@

[**Competing Interests Statement:**]{.underline} Dr. Wang has consulted ad hoc for Exponent Inc. and MITRE a federally funded research center for the Centers for Medicare and Medicaid Services on unrelated work. Dr. Schneeweiss is participating in investigator-initiated grants to the Brigham and Women's Hospital from Boehringer Ingelheim, Takeda, and UCB unrelated to the topic of this study. He owns equity in Aetion Inc., a software manufacturer. He is an advisor to Temedica GmbH, a patient-oriented data generation company. His interests were declared, reviewed, and approved by the Brigham and Women's Hospital in accordance with their institutional compliance policies.

@@

[***Proposed target journals:***]{.underline} *JCO CCI =\> JAMA Network Open =\> CPT*

@@

**Systematic process for understanding the validity of RWE for oncology submissions**

@@

@@

::: landscape

@@

```{r}
#| label: fig-process
#| fig-cap: "Systematic process to understand effectiveness claims of oncology trials using real-world evidence."
#| fig-cap-location: top
#| fig-width: 12

knitr::include_graphics(here("figures", "process.png"))
```

[View figure in higher resolution]()
:::
